Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation

### 2020-03-14 analysis/paper.Rmd
Cleaning up comments

```{r set working directory, include=TRUE}
#setwd(dirname(rstudioapi::getSourceEditorContext()$path))
#getwd()
library(here)
```

@@

```{r replication ANOVA  test, include=TRUE, echo=FALSE}
lances_ANOVA_site<-procD.allometry(shape ~ size, ~site, print.progress = FALSE,  data=lances_geomorph,method="PredLine")

@@

```{r explore ANOVA  test v1, include=TRUE, echo=FALSE}
lances_ANOVA_two<-procD.allometry(shape ~ size, ~site, logsz=FALSE, seed=42, alpha=0.1, print.progress = FALSE,  data=lances_geomorph, method="PredLine")

@@

```{r explore ANOVA  test v2, include=TRUE, echo=FALSE}
lances_ANOVA_three <- procD.allometry(shape ~ size, ~site, logsz=FALSE, seed=42, alpha=0.1, effect.type="cohen", RRPP=FALSE,  print.progress = FALSE, data=lances_geomorph, method="PredLine")

>>>>

```{r set working directory, include=TRUE}
#previous solutions used before moving to the here package commented out below
#setwd(dirname(rstudioapi::getSourceEditorContext()$path))
#getwd()

library(here)
```

@@

```{r replication ANOVA  test, include=TRUE, echo=FALSE}
#
lances_ANOVA_site<-procD.allometry(shape ~ size, ~site, print.progress = FALSE,  data=lances_geomorph,method="PredLine")

@@

```{r explore ANOVA  test v1, include=TRUE, echo=FALSE}
#
lances_ANOVA_two<-procD.allometry(shape ~ size, ~site, logsz=FALSE, seed=42, alpha=0.1, print.progress = FALSE,  data=lances_geomorph, method="PredLine")

@@

```{r explore ANOVA  test v2, include=TRUE, echo=FALSE}
#procD.allometry geomorph anova. needs geomorph 3.0.6!
lances_ANOVA_three <- procD.allometry(shape ~ size, ~site, logsz=FALSE, seed=42, alpha=0.1, effect.type="cohen", RRPP=FALSE,  print.progress = FALSE, data=lances_geomorph, method="PredLine")
